Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
update interoperability
update visibility

Definition \ref{VisibilitySelected} rephrased: The extent to which all of the
steps \wss{What are all the steps?} and the current status of a software
development process are documented clearly. \wss{I wonder if rather than
  ``documented clearly'', we should be more abstract and talk about how these
  things can be easily determined.  Documentation is probably how the
  information will be conveyed, but it doesn't have to be how it is done.}

>>>>

Definition \ref{VisibilitySelected} rephrased: The extent to which all of the
steps of a software development process and the current status of it are 
conveyed clearly. \wss{I wonder if rather than
  ``documented clearly'', we should be more abstract and talk about how these
  things can be easily determined.  Documentation is probably how the
  information will be conveyed, but it doesn't have to be how it is done.}
